---
title: "Stress x EE MA"
authors: "Erin L Macartney, Malgorzata Lagisz, Shinichi Nakagawa"
date: "01/07/2021"
output:
  html_document:
    code_folding: hide
    df_print: kable
    toc: TRUE
    toc_float: TRUE
    toc_depth: 4
    collapsed: FALSE
    YAML: rmdformats::robobook
---

#### Loading packages

```{r, message = FALSE, warning = FALSE, results = 'hide'}

knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(tidyverse, 
               here,
               metafor,
               emmeans,
               orchaRd, 
               MCMCglmm,
               corpcor,
               clubSandwich,
               MuMIn, 
               patchwork,
               naniar,
               GoodmanKruskal,
               networkD3,
               ggplot2,
               ggalluvial,
               ggthemr,
               cowplot)
# needed for model selection using MuMin within metafor
eval(metafor:::.MuMIn)

```

#### Loading data and functions

```{r, message = FALSE, warning = FALSE, results = 'hide'}
dat <- read_csv(here("Data","Full_data.csv"))
# Load custom function to extract data 
#source(here("R/functions.R")) 
source(here("R/functions_cleanedup.R")) 
```

#### Data organisation
Getting effect sizes from function, 'flipping' effect sizes so that all effect sizes are higher values = individuals do better and learning/memory, and shifting negative values to positive as lnRR cannot use negative values

```{r, message = FALSE, warning = FALSE, results = 'hide'}
#removing study with negative values as these are unable to be used for lnRR
dat <- droplevels(dat[!dat$First_author == 'Wang',])

#Getting effect sizes
effect_size <- effect_set(CC_n = "CC_n", CC_mean = "CC_mean", CC_SD = "CC_SD",
                          EC_n = "EC_n", EC_mean = "EC_mean" , EC_SD ="EC_SD",
                          CS_n = "CS_n", CS_mean = "CS_mean", CS_SD = "CS_SD",
                          ES_n = "ES_n", ES_mean = "ES_mean", ES_SD = "ES_SD",
                          data = dat)
#'pure' effect sizes
effect_size2 <- effect_set2(CC_n = "CC_n", CC_mean = "CC_mean", CC_SD = "CC_SD",
                          EC_n = "EC_n", EC_mean = "EC_mean" , EC_SD ="EC_SD",
                          CS_n = "CS_n", CS_mean = "CS_mean", CS_SD = "CS_SD",
                          ES_n = "ES_n", ES_mean = "ES_mean", ES_SD = "ES_SD",
                          data = dat) 

#Removing missing effect sizes
dim(dat)
full_info <- which(complete.cases(effect_size) == TRUE)
dat_effect <- cbind(dat, effect_size, effect_size2)
dat <- dat_effect[full_info, ]
names(dat_effect)
dat <- dat_effect[full_info, ]

dim(dat_effect)
dimentions <- dim(dat) 

#Flipping 'lower is better' effect sizes
#flipping lnRR for values where higher = worse
dat$lnRR_Ea <- ifelse(dat$Response_direction == 2, dat$lnRR_E*-1,ifelse(is.na(dat$Response_direction) == TRUE, NA, dat$lnRR_E)) # currently NAswhich causes error
dat$lnRR_Sa  <- ifelse(dat$Response_direction == 2, dat$lnRR_S*-1,ifelse(is.na(dat$Response_direction) == TRUE, NA, dat$lnRR_S)) # currently NAswhich causes error
dat$lnRR_ESa <-  ifelse(dat$Response_direction == 2, dat$lnRR_ES*-1,ifelse(is.na(dat$Response_direction) == TRUE, NA, dat$lnRR_ES)) # currently NAswhich causes error

#flipping 'pure effect sizes'
dat$lnRR_E2a <- ifelse(dat$Response_direction == 2, dat$lnRR_E2*-1,ifelse(is.na(dat$Response_direction) == TRUE, NA, dat$lnRR_E2)) # currently NAswhich causes error
dat$lnRR_S2a  <- ifelse(dat$Response_direction == 2, dat$lnRR_S2*-1,ifelse(is.na(dat$Response_direction) == TRUE, NA, dat$lnRR_S2)) # currently NAswhich causes error
dat$lnRR_ES2a <-  ifelse(dat$Response_direction == 2, dat$lnRR_ES2*-1,ifelse(is.na(dat$Response_direction) == TRUE, NA, dat$lnRR_ES2)) # currently NAswhich causes error
dat$lnRR_E3a <-  ifelse(dat$Response_direction == 2, dat$lnRR_E3*-1,ifelse(is.na(dat$Response_direction) == TRUE, NA, dat$lnRR_E3)) # currently NAswhich causes error
dat$lnRR_S3a <-  ifelse(dat$Response_direction == 2, dat$lnRR_S3*-1,ifelse(is.na(dat$Response_direction) == TRUE, NA, dat$lnRR_S3)) # currently NAswhich causes error

#flipping SMD
dat$SMD_Ea <- ifelse(dat$Response_direction == 2, dat$SMD_E*-1,ifelse(is.na(dat$Response_direction) == TRUE, NA, dat$SMD_E)) # currently NAswhich causes error
dat$SMD_Sa  <- ifelse(dat$Response_direction == 2, dat$SMD_S*-1,ifelse(is.na(dat$Response_direction) == TRUE, NA, dat$SMD_S)) # currently NAswhich causes error
dat$SMD_ESa <-  ifelse(dat$Response_direction == 2, dat$SMD_ES*-1,ifelse(is.na(dat$Response_direction) == TRUE, NA, dat$SMD_ES))

#rounding down integer sample sizes 
dat$CC_n <- floor(dat$CC_n)
dat$EC_n <- floor(dat$EC_n)
dat$CS_n <- floor(dat$CS_n)
dat$ES_n <- floor(dat$CS_n)
```

#### Assigning human readable words to moderators
```{r, message = FALSE, warning = FALSE, results = 'hide'}
dat <- dat %>% mutate(Type_learning = case_when(Type_learning == 1 ~ "Habituation",
                                                Type_learning == 2 ~ "Conditioning",
                                                Type_learning == 3 ~ "Recognition", 
                                                Type_learning == 4 ~ "Unclear"),
                      Learning_vs_memory = case_when(Learning_vs_memory == 1 ~ "Learning",
                                                     Learning_vs_memory == 2 ~ "Memory", 
                                                     Learning_vs_memory == 1 ~ "Unclear"),
                      Appetitive_vs_aversive = case_when(Appetitive_vs_aversive == 1 ~"Appetitive",
                                                         Appetitive_vs_aversive == 2 ~ "Aversive",
                                                         Appetitive_vs_aversive == 3 ~ "Not applicable",
                                                         Appetitive_vs_aversive == 4 ~ "Unclear"),
                      Type_stress_exposure = case_when(Type_stress_exposure == 1 ~ "Density",
                                                       Type_stress_exposure == 2 ~ "Scent",
                                                       Type_stress_exposure == 3 ~ "Shock",
                                                       Type_stress_exposure == 4 ~ "Exertion",
                                                       Type_stress_exposure == 5 ~ "Restraint",
                                                       Type_stress_exposure == 6 ~ "MS",
                                                       Type_stress_exposure == 7 ~ "Circadian rhythm",
                                                       Type_stress_exposure == 8 ~ "Noise",
                                                       Type_stress_exposure == 9 ~ "Other",
                                                       Type_stress_exposure == 10 ~ "Combination",
                                                       Type_stress_exposure == 11 ~ "unclear"), 
                      Age_stress_exposure = case_when(Age_stress_exposure == 1 ~ "Prenatal",
                                                      Age_stress_exposure == 2 ~ "Early postnatal",
                                                      Age_stress_exposure == 3 ~ "Adolescent",
                                                      Age_stress_exposure == 4 ~ "Adult",
                                                      Age_stress_exposure == 5 ~ "Unclear"),
                      Stress_duration = case_when(Stress_duration == 1 ~ "Acute",
                                                  Stress_duration == 2 ~ "Chronic",
                                                  Stress_duration == 3 ~ "Intermittent",
                                                  Stress_duration == 4 ~ "Unclear"),
                      EE_social = case_when(EE_social == 1 ~ "Social",
                                            EE_social== 2 ~ "Non-social", 
                                            EE_social == 3 ~ "Unclear"), 
                      EE_exercise = case_when(EE_exercise == 1 ~ "Exercise", 
                                              EE_exercise == 2 ~ "No exercise"),
                      Age_EE_exposure = case_when(Age_EE_exposure == 1 ~ "Prenatal", 
                                                  Age_EE_exposure == 2 ~ "Early postnatal",
                                                  Age_EE_exposure == 3 ~ "Adolescent", 
                                                  Age_EE_exposure == 4 ~ "Adult",
                                                  Age_EE_exposure == 5 ~ "Unclear"),
                      Stress_vs_EE_timing = case_when(Stress_vs_EE_timing == 1 ~ "Stress first",
                                                      Stress_vs_EE_timing == 2 ~ "Enrichment first",
                                                      Stress_vs_EE_timing == 3 ~ "Concurrently", 
                                                      Stress_vs_EE_timing == 4 ~ "Unclear"))

```

# Data exploration

### General  

``` {r, message = FALSE, warning = FALSE}
#Number of effect sizes
length(unique(dat$ES_ID))  

#Number of studies
length(unique(dat$Study_ID))

#Publication years
min(dat$Year_published) 
max(dat$Year_published)

```
### Explore associations among predictor variables   

```{r exploratory plots, results = 'hide'}
#see columns with missing values
vis_miss(dat) +
  theme(plot.title = element_text(hjust = 0.5, vjust = 3), 
        plot.margin = margin(t = 0.5, r = 3, b = 1, l = 1, unit = "cm")) +
  ggtitle("Missing data in the selected predictors") #no mising values


#useGoodman and Kruskal’s τ measure of association between categorical predictor variables (function from package GoodmanKruskal: https://cran.r-project.org/web/packages/GoodmanKruskal/vignettes/GoodmanKruskal.html)
#GKmatrix <- GKtauDataframe(subset(dat, select = c("Sex", "Type_learning", "Learning_vs_memory", #"Appetitive_vs_aversive",  "Type_stress_exposure", "Age_stress_exposure", "Stress_duration", #"EE_social_HR", "EE_exercise", "Age_EE_exposure", "Stress_vs_EE_timing", "Age_assay")))
#plot(GKmatrix)

#simple pairwise contingency tables
table(dat$Type_learning, dat$Appetitive_vs_aversive) 
table(dat$Age_stress_exposure, dat$Age_EE_exposure) 
table(dat$Type_stress_exposure, dat$Age_stress_exposure)
table(dat$Type_stress_exposure, dat$Age_assay)
table(dat$Type_stress_exposure, dat$Stress_duration)
```

### Alluvial diagrams  

```{r alluvial plots species strains sex, results = 'hide'}
#Species, strain and sex variables  

# TODO - you need to break up to different chuncks and how different plots - probably use tabs - you can look at Patrice's Rmd file - which show how to do mulitple tabs - which is very good way to show this kind of things


# create a frequency table for Species and Strain variables
freq_1 <- as.data.frame(table(dat$Common_species, dat$Strain)) %>% rename(Species = Var1, Strain = Var2)

is_alluvia_form(as.data.frame(freq_1), axes = 1:2, silent = TRUE)

ggplot(data = freq_1,
  aes(axis1 = Species, axis2 = Strain, y = Freq)) +
  geom_alluvium(aes(fill = Strain)) +
  geom_stratum(aes(fill = Species)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
#theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Species", "Strain"), expand = c(0.15, 0.05), position = "top") +
  ggtitle("Species and strains used (set1)")


# create frequency table for Sex, Species and Strain
freq_2 <- as.data.frame(table(dat$Sex, dat$Common_species, dat$Strain)) %>% rename(Sex = Var1, Species = Var2, Strain = Var3)
is_alluvia_form(as.data.frame(freq_2), axes = 1:3, silent = TRUE)

ggplot(data = freq_2,
  aes(axis1 = Sex, axis2 = Species, axis3 = Strain, y = Freq)) +
  geom_alluvium(aes(fill = Sex)) +
  geom_flow() +
  geom_stratum(aes(fill = Sex)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  #theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Sex", "Species", "Strain"), expand = c(0.15, 0.05), position = "top") +
  ggtitle("Species, strains and sex used (set2)")

freq_2 %>% filter(Freq != 0) %>% arrange(desc(Freq)) #collapesd table of values, without 0s

#Age (life stages) variables 
freq_ages1 <- as.data.frame(table(dat$Age_stress_exposure, dat$Age_EE_exposure)) %>% rename(Age_stress = Var1, Age_EE = Var2)
is_alluvia_form(as.data.frame(freq_ages1), axes = 1:2, silent = TRUE)

ggplot(data = freq_ages1,
  aes(axis1 = Age_stress, axis2 = Age_EE, y = Freq)) +
  geom_alluvium(aes(fill = Age_EE)) +
  geom_stratum(aes(fill = Age_stress)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
#theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Stress", "Enrichment"), expand = c(0.15, 0.05), position = "top") +
  ggtitle("Life stages used (set1)")


freq_ages2 <- as.data.frame(table(dat$Age_stress_exposure, dat$Age_EE_exposure, dat$Age_assay)) %>% rename(Age_stress = Var1, Age_EE = Var2, Age_assay = Var3)

is_alluvia_form(as.data.frame(freq_ages2), axes = 1:3, silent = TRUE)

ggplot(data = freq_ages2,
  aes(axis1 = Age_stress, axis2 = Age_EE, axis3 = Age_assay, y = Freq)) +
  geom_alluvium(aes(fill = Age_stress)) +
  geom_flow() +
  geom_stratum(aes(fill = Age_stress)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  #theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Stress", "Enrichment", "Assay"), expand = c(0.15, 0.05), position = "top") +
  ggtitle("Life stages used (set2)")

freq_ages2 %>% filter(Freq != 0) %>% arrange(desc(Freq)) #collapesd table of values, without 0s

freq_ages3 <- as.data.frame(table(dat$Age_stress_exposure, dat$Age_EE_exposure, dat$Age_assay, dat$Stress_vs_EE_timing)) %>% rename(Age_stress = Var1, Age_EE = Var2, Age_assay = Var3, Order = Var4)
is_alluvia_form(as.data.frame(freq_ages3), axes = 1:4, silent = TRUE)

ggplot(data = freq_ages3,
  aes(axis1 = Age_stress, axis2 = Age_EE, axis3 = Age_assay, axis4 = Order,  y = Freq)) +
  geom_alluvium(aes(fill = Age_stress)) +
  geom_flow() +
  geom_stratum(aes(fill = Age_stress)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  #theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Stress", "Enrichment", "Assay", "Order"), expand = c(0.15, 0.05), position = "top") +
  ggtitle("Life stages used and order (set3)")

freq_ages2 %>% filter(Freq != 0) %>% arrange(desc(Freq)) #collapesd table of values, without 0s
freq_ages3 %>% filter(Freq != 0) %>% arrange(desc(Freq)) #collapesd table of values, without 0s

#Stress variables
freq_stress1 <- as.data.frame(table(dat$Stress_duration, dat$Type_stress_exposure)) %>% rename(Stress_duration = Var1,  Stress_type = Var2)
is_alluvia_form(as.data.frame(freq_stress1), axes = 1:2, silent = TRUE)

ggplot(data = freq_stress1,
  aes(axis1 = Stress_duration, axis2 = Stress_type, y = Freq)) +
  geom_alluvium(aes(fill = Stress_duration)) +
  geom_stratum(aes(fill = Stress_duration)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
#theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Duration", "Type"), expand = c(0.15, 0.05), position = "top") +
  ggtitle("Stress exposure  variables (set1)")

# create frequency table for 3 categorical Stress variables
freq_stress2 <- as.data.frame(table(dat$Age_stress_exposure, dat$Stress_duration, dat$Type_stress_exposure)) %>% rename(Age_stress = Var1, Duration_stress = Var2, Type_stress = Var3)
is_alluvia_form(as.data.frame(freq_stress2), axes = 1:3, silent = TRUE)

ggplot(data = freq_stress2,
  aes(axis1 = Age_stress, axis2 = Duration_stress, axis3 = Type_stress, y = Freq)) +
  geom_alluvium(aes(fill = Age_stress)) +
  geom_flow() +
  geom_stratum(aes(fill = Age_stress)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  #theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Age", "Duration", "Type"), expand = c(0.1, 0.1), position = "top") +
  ggtitle("Stress exposure variables (set2)")

#EE variables 
freq_EE1 <- as.data.frame(table(dat$EE_exercise, dat$EE_social)) %>% rename(EE_exercise = Var1, EE_social = Var2)
is_alluvia_form(as.data.frame(freq_stress1), axes = 1:2, silent = TRUE)

ggplot(data = freq_EE1,
  aes(axis1 = EE_exercise, axis2 = EE_social, y = Freq)) +
  geom_alluvium(aes(fill = EE_exercise)) +
  geom_stratum(aes(fill = EE_exercise)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
#theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Exercise", "Social"), expand = c(0.15, 0.05), position = "top") +
  ggtitle("EE exposure  variables (set1)")


# create frequency table for 3 categorical EE variables
freq_EE2 <- as.data.frame(table(dat$Age_EE_exposure, dat$EE_exercise, dat$EE_social)) %>% rename(Age_EE = Var1, EE_exercise = Var2, EE_social = Var3)
is_alluvia_form(as.data.frame(freq_EE2), axes = 1:3, silent = TRUE)

ggplot(data = freq_EE2,
  aes(axis1 = Age_EE, axis2 = EE_exercise, axis3 = EE_social, y = Freq)) +
  geom_alluvium(aes(fill = Age_EE)) +
  geom_flow() +
  geom_stratum(aes(fill = Age_EE)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  #theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Age", "Exercise", "Social"), expand = c(0.1, 0.1), position = "top") +
  ggtitle("EE exposure variables (set2)")

#assay variables
freq_assay1 <- as.data.frame(table(dat$Learning_vs_memory, dat$Appetitive_vs_aversive)) %>% rename(Learning_Memory = Var1, Reinforcement = Var2)
is_alluvia_form(as.data.frame(freq_assay1), axes = 1:2, silent = TRUE)

ggplot(data = freq_assay1,
  aes(axis1 = Learning_Memory, axis2 = Reinforcement, y = Freq)) +
  geom_alluvium(aes(fill = Learning_Memory)) +
  geom_stratum(aes(fill = Learning_Memory)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
#theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Learning_Memory", "Reinforcement"), expand = c(0.15, 0.05), position = "top") +
  ggtitle("Behavioural assay  variables (set1)")


# create frequency table for 3 categorical assay variables
freq_assay2 <- as.data.frame(table(dat$Age_assay, dat$Learning_vs_memory, dat$Appetitive_vs_aversive)) %>% rename(Age_assay = Var1, Learning_Memory = Var2, Reinforcement = Var3)
is_alluvia_form(as.data.frame(freq_assay2), axes = 1:3, silent = TRUE)

ggplot(data = freq_assay2,
  aes(axis1 = Age_assay, axis2 = Learning_Memory, axis3 = Reinforcement, y = Freq)) +
  geom_alluvium(aes(fill = Age_assay)) +
  geom_flow() +
  geom_stratum(aes(fill = Age_assay)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  #theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Age", "Learning_Memory", "Reinforcement"), expand = c(0.1, 0.1), position = "top") +
  ggtitle("Behavioural assay  variables (set2)")


# create frequency table for another 3 categorical assay variables
freq_assay3 <- as.data.frame(table(dat$Type_learning, dat$Learning_vs_memory, dat$Appetitive_vs_aversive)) %>% rename(Type = Var1, Learning_Memory = Var2, Reinforcement = Var3)
is_alluvia_form(as.data.frame(freq_assay3), axes = 1:3, silent = TRUE)

ggplot(data = freq_assay3,
  aes(axis1 = Type, axis2 = Learning_Memory, axis3 = Reinforcement, y = Freq)) +
  geom_alluvium(aes(fill = Type)) +
  geom_flow() +
  geom_stratum(aes(fill = Type)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  #theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Type", "Learning_Memory", "Reinforcement"), expand = c(0.1, 0.1), position = "top") +
  ggtitle("Behavioural assay  variables (set3)")
```


#### Making Variance VCV
Used to control for trait relatedness within individuals

``` {r, message = FALSE, warning = FALSE, results = 'hide'}
##adding data to empty VCV matrix

VCV_E <- impute_covariance_matrix(vi = dat$lnRRV_E, cluster = dat$Study_ID, r = 0.5)
VCV_S <- impute_covariance_matrix(vi = dat$lnRRV_S, cluster = dat$Study_ID, r = 0.5)
VCV_ES <- impute_covariance_matrix(vi = dat$lnRRV_ES, cluster = dat$Study_ID, r = 0.5)

VCV_Ea <- impute_covariance_matrix(vi = dat$SMDV_E, cluster = dat$Study_ID, r = 0.5)
VCV_Sa <- impute_covariance_matrix(vi = dat$SMDV_S, cluster = dat$Study_ID, r = 0.5)
VCV_ESa <- impute_covariance_matrix(vi = dat$SMDV_ES, cluster = dat$Study_ID, r = 0.5)

```

#### Examining the group of large/positive effect sizes
Note that I checked the top four most positive interaction effect sizes and the data looks correct.
Highest ES is study 27, effect size 88, where Maternally separated EE individuals freeze significantly more when given a cue from inhibitory avoidance. 
Im not sure why the second highest one (ES 16) is so high as the control indivs do the best. 
EE indivs do best in the 3rd highest ES (ES 10) so not sure about this one either?
The fourth highest (ES 12) seems correct
``` {r, message = FALSE, warning = FALSE}
largeES_S <- dat %>%
  slice_max(lnRR_S, n = 10)

largeES_E <- dat %>%
  slice_max(lnRR_E, n = 10)

largeES_ES <-dat %>%
  slice_max(lnRR_ES, n = 10)

#most of the largest effect sizes come from different papers

````

# Modelling with lnRR
Things todo: 
- Incorporate strain as random effect
- Consider including VCV
- Check  outlier
- Remove moderator levels with k < 5

## Environmental enrichment

### Intercept model
Learning and memory are significantly improved when housed with environmnetal enrichment

``` {r, message = FALSE, warning = FALSE}
mod_E0 <- rma.mv(yi = lnRR_Ea, V = VCV_E, random = list(~1|Study_ID,
                                                          ~1|ES_ID,
                                                          ~1|Strain),
                 test = "t",
                 data = dat)
summary(mod_E0) 
i2_ml(mod_E0) 

#trying orchard plot

orchard_plot(mod_E0, mod = "Int", xlab = "lnRR", alpha=0.4) +  # Orchard plot 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5)+ # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2)+ # confidence intervals
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  scale_colour_manual(values = "darkorange")+ # change colours
  scale_fill_manual(values="darkorange")+ 
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        text = element_text(size = 24), # change font sizes
        legend.title = element_text(size = 15),
        legend.text = element_text(size = 13)) 
```

### Meta-regression

#### Type of learning
The type of learning/memory response

``` {r, message = FALSE, warning = FALSE}
dat1 <- filter(dat, Type_learning %in% c("Recognition", "Habituation", "Conditioning"))
VCV_E1 <- impute_covariance_matrix(vi = dat1$lnRRV_E, cluster = dat$Study_ID, r = 0.5)

mod_E1 <- rma.mv(yi = lnRR_Ea, V = VCV_E1, mod = ~Type_learning-1, random = list(~1|Study_ID,
                                                                                  ~1|ES_ID,
                                                                                  ~1|Strain),
                 test = "t",
                 data = dat1)

summary(mod_E1)
r2_ml(mod_E1) 

# Orchard plot 
Learning_E <- orchard_plot(mod_E1, mod = "Type_learning", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  xlim(-0.5, 2) + 
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        text = element_text(size = 15), # change font sizes
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10)) 
```

#### Learning vs Memory
Is the assay broadly measuring learning or memory? 

``` {r, message = FALSE, warning = FALSE}
mod_E2 <-  rma.mv(yi = lnRR_Ea, V = VCV_E, mod = ~Learning_vs_memory-1, random = list(~1|Study_ID,
                                                                                        ~1|ES_ID,
                                                                                        ~1|Strain),
                  test = "t",
                  data = dat)

summary(mod_E2) 
r2_ml(mod_E2) 

# Orchard plot 
LvsM_E<- orchard_plot(mod_E2, mod = "Learning_vs_memory", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  xlim(-0.5, 2) + 
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        text = element_text(size = 15), # change font sizes
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10)) 
```

#### Type of reinforcement 
The type of cue used 

``` {r, message = FALSE, warning = FALSE}

dat2 <- filter(dat, Appetitive_vs_aversive %in% c("Appetitive", "Aversive", "Not applicable"))
VCV_E2 <- impute_covariance_matrix(vi = dat2$lnRRV_E, cluster = dat2$Study_ID, r = 0.5)
mod_E3 <- rma.mv(yi = lnRR_Ea, V = VCV_E2, mod = ~ Appetitive_vs_aversive-1, random = list(~1|Study_ID,
                                                                                            ~1|ES_ID,
                                                                                            ~1|Strain),
                 test = "t",
                 data = dat2)

summary(mod_E3)
r2_ml(mod_E3) 

# Orchard plot 
Reinforcement_E <-orchard_plot(mod_E3, mod = "Appetitive_vs_aversive", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  xlim(-0.5, 2) + 
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        text = element_text(size = 15), # change font sizes
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10)) 
````

#### Social enrichment
Does EE also include a manipulation of social environment? Note that we excluded any studies that exclusively used social enrichment.s

``` {r, message = FALSE, warning = FALSE}
dat5 <- filter(dat, EE_social %in% c("Social", "Non-social"))
VCV_E5 <- impute_covariance_matrix(vi = dat5$lnRRV_E, cluster = dat$Study_ID, r = 0.5)
  
mod_E4<- rma.mv(yi = lnRR_Ea, V = VCV_E5, mod = ~EE_social-1, random = list(~1|Study_ID, 
                                                                             ~1|ES_ID,
                                                                             ~1|Strain),
                test = "t",data = dat5)

summary(mod_E4)
r2_ml(mod_E4) 

# Orchard plot 
Social_E <-orchard_plot(mod_E4, mod = "EE_social", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  xlim(-0.5, 2) + 
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
       text = element_text(size = 15), # change font sizes
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10)) 
```

#### Exercise enrichment
Does the form of enrichment include exercise through a running wheel or treadmill?

``` {r, message = FALSE, warning = FALSE}
mod_E5<- rma.mv(yi = lnRR_Ea, V = VCV_E, mod = ~EE_exercise-1, random = list(~1|Study_ID,
                                                                               ~1|ES_ID,
                                                                               ~1|Strain),
                test = "t",
                data = dat)

summary(mod_E5)
r2_ml(mod_E5) 

# Orchard plot 
Exercise_E <-orchard_plot(mod_E5, mod = "EE_exercise", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  xlim(-0.5, 2) + 
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        text = element_text(size = 15), # change font sizes
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10)) 
```
#### Age of enrichment
The age at which the individuals were exposed to environmental enrichment.
``` {r, message = FALSE, warning = FALSE}
dat6 <- filter(dat, Age_EE_exposure %in% c("Adult", "Adolescent"))
VCV_E6 <- impute_covariance_matrix(vi = dat6$lnRRV_E, cluster = dat6$Study_ID, r = 0.5)


mod_E6 <- rma.mv(yi = lnRR_Ea, V = VCV_E6, mod = ~Age_EE_exposure-1, random = list(~1|Study_ID,
                                                                                    ~1|ES_ID,
                                                                                    ~1|Strain),
                 test = "t",
                 data = dat6)

summary(mod_E6) 
r2_ml(mod_E6) 

#Orchard plot 
Age_E<- orchard_plot(mod_E6, mod = "Age_EE_exposure", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  xlim(-0.5, 2) + 
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        text = element_text(size = 15), # change font sizes
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))  
```

### Full model
``` {r, message = FALSE, warning = FALSE}
#filter data so that all K < 5 are removed
dat_Efm <- dat %>%
  filter(Type_learning %in% c("Recognition", "Habituation", "Conditioning"),
         Appetitive_vs_aversive %in% c("Appetitive", "Aversive", "Not applicable"),
         EE_social %in% c("Social", "Non-social"), 
         Age_EE_exposure %in% c("Adult", "Adolescent"))

VCV_Efm <- impute_covariance_matrix(vi = dat_Efm$lnRRV_E, cluster = dat$Study_ID, r = 0.5)
                 
mod_Efm <- rma.mv(yi = lnRR_Sa, V = VCV_Efm, mod = ~Type_learning-1 + Learning_vs_memory-1 + Appetitive_vs_aversive-1 + EE_social-1 + EE_exercise-1 + Age_EE_exposure-1 , random =   list(~1|Study_ID,
                                                                                    ~1|ES_ID,
                                                                                    ~1|Strain),
                    test = "t",
                 data = dat_Efm)
summary(mod_Efm)
r2_ml(mod_Efm) 

res_Efm <- dredge(mod_Efm, trace=2)
res_Efm2<- subset(res_Efm, delta <= 6, recalc.weights=FALSE)
importance(res_Efm2)
```

### Publication bias & sensitivity analysis
``` {r, message = FALSE, warning = FALSE}
funnel(mod_Efm)

#year published was scaled previously  under stress PB

dat_Efm$sqrt_inv_e_n <- with(dat_Efm, sqrt(1/CC_n + 1/EC_n + 1/ES_n + 1/CS_n))

PB_MR_E<- rma.mv(lnRR_Sa, lnRRV_S, mods = ~1 + sqrt_inv_e_n +  Year_published + Type_learning + Appetitive_vs_aversive + EE_social + EE_exercise + Age_stress_exposure, random = list(~1|Study_ID,
                                                          ~1|ES_ID,
                                                          ~1|Strain), method = "REML", test = "t", 
    data = dat_Efm)

estimates_PB_MR_E<- estimates.CI(PB_MR_E)
estimates_PB_MR_E

#no effect of inv_effective sample size or year published

#leave-one-out analysis
dat$Study_ID <- as.factor(dat$Study_ID)

LeaveOneOut_effectsize <- list()
for(i in 1:length(levels(dat$Study_ID))){
  LeaveOneOut_effectsize[[i]] <- rma.mv(yi = lnRR_Ea, V = lnRRV_E, 
                                        random = list(~1 | Study_ID,~1| ES_ID, ~1 | Strain), 
                                        method = "REML", data = dat[dat$Study_ID
                                                                    != levels(dat$Study_ID)[i], ])}


# writing function for extracting est, ci.lb, and ci.ub from all models
est.func <- function(mod_E0){
  df <- data.frame(est = mod_E0$b, lower = mod_E0$ci.lb, upper = mod_E0$ci.ub)
  return(df)
}


#using dplyr to form data frame
MA_CVR <- lapply(LeaveOneOut_effectsize, function(x) est.func(x))%>% bind_rows %>% mutate(left_out = levels(dat$Study_ID))

#telling ggplot to stop reordering factors
MA_CVR$left_out<- as.factor(MA_CVR$left_out)
MA_CVR$left_out<-factor(MA_CVR$left_out, levels = MA_CVR$left_out)

#plotting
leaveoneout_E <- ggplot(MA_CVR) +
  geom_hline(yintercept = 0, lty = 2, lwd = 1) +
  geom_hline(yintercept = mod_E0$ci.lb, lty = 3, lwd = 0.75, colour = "black") +
  geom_hline(yintercept = mod_E0$b, lty = 1, lwd = 0.75, colour = "black") +
  geom_hline(yintercept = mod_E0$ci.ub, lty = 3, lwd = 0.75, colour = "black") +
  geom_pointrange(aes(x = left_out, y = est, ymin = lower, ymax = upper)) +
  xlab("Study left out") + 
  ylab("lnRR, 95% CI") + 
  coord_flip() +
  theme(panel.grid.minor = element_blank())+
  theme_bw() + theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor.x = element_blank() ) +
  theme(axis.text.y = element_text(size = 6))

leaveoneout_E

dat$Study_ID <- as.integer(dat$Study_ID)
```

## Stress

### Intercept model
Learning and memory are significantly reduced due to stress. 
High heterogeneity

``` {r, message = FALSE, warning = FALSE}
mod_S0 <- rma.mv(yi = lnRR_Sa, V = VCV_S, random = list(~1|Study_ID,
                                                          ~1|ES_ID,
                                                          ~1|Strain),
                 test = "t", 
                 data = dat)

summary(mod_S0) 
i2_ml(mod_S0) 

orchard_plot(mod_S0, mod = "Int", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        text = element_text(size = 24), # change font sizes
        legend.title = element_text(size = 15),
        legend.text = element_text(size = 13)) 
```

### Meta-regression

#### Type of learning
The type of learning/memory response 

``` {r, message = FALSE, warning = FALSE}
dat$Type_learning<-as.factor(dat$Type_learning)

VCV_S1 <- impute_covariance_matrix(vi = dat1$lnRRV_S, cluster = dat$Study_ID, r = 0.5)


mod_S1 <- rma.mv(yi = lnRR_Sa, V = VCV_S1, mod = ~Type_learning-1, random =   list(~1|Study_ID,
                                                                                    ~1|ES_ID,
                                                                                    ~1|Strain),
                 test = "t",
                 data = dat1)

summary(mod_S1)
r2_ml(mod_S1) 

# Orchard plot 
Learning_S <-orchard_plot(mod_S1, mod = "Type_learning", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        text = element_text(size = 15), # change font sizes
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10)) 
```

#### Learning vs Memory
Is the assay broadly measuring learning or memory? 

``` {r, message = FALSE, warning = FALSE}

mod_S2 <-  rma.mv(yi = lnRR_Sa, V = VCV_S, mod = ~Learning_vs_memory-1, random = list(~1|Study_ID,
                                                                                        ~1|ES_ID,
                                                                                        ~1|Strain),
                  test = "t",
                  data = dat)

summary(mod_S2) 
r2_ml(mod_S2) 

# Orchard plot 
LvsM_S <- orchard_plot(mod_S2, mod = "Learning_vs_memory", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
       text = element_text(size = 15), # change font sizes
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10)) 
```

#### Type of reinforcement
The type of cue used 

``` {r, message = FALSE, warning = FALSE}

VCV_S2 <- VCV_E <- impute_covariance_matrix(vi = dat2$lnRRV_S, cluster = dat$Study_ID, r = 0.5)

mod_S3 <- rma.mv(yi = lnRR_Sa, V = VCV_S2, mod = ~ Appetitive_vs_aversive-1, random = list(~1|Study_ID,
                                                                                            ~1|ES_ID,
                                                                                            ~1|Strain),
                 test = "t",
                 data = dat2)

summary(mod_S3)
r2_ml(mod_S3) 

# Orchard plot 
Reinforcement_S <-orchard_plot(mod_S3, mod = "Appetitive_vs_aversive", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
       text = element_text(size = 15), # change font sizes
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10)) 
````

#### Type of stress
The type of stress manipulation 

``` {r, message = FALSE, warning = FALSE}
dat3 <- filter(dat, Type_stress_exposure %in% c("Restraint", "Noise", "MS", "Combination"))
VCV_S3 <- impute_covariance_matrix(vi = dat3$lnRRV_S, cluster = dat$Study_ID, r = 0.5)

mod_S4 <- rma.mv(yi = lnRR_Sa, V = VCV_S3, mod = ~Type_stress_exposure-1, random = list(~1|Study_ID,
                                                                                         ~1|ES_ID,
                                                                                         ~1|Strain),
                 test = "t",
                 data = dat3)
summary(mod_S4) 
r2_ml(mod_S4)

# Orchard plot 
Stressor<- orchard_plot(mod_S4, mod = "Type_stress_exposure", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        text = element_text(size = 15), # change font sizes
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10)) 
````

#### Age of stress
``` {r, message = FALSE, warning = FALSE}
VCV_S3a <- impute_covariance_matrix(vi = dat$lnRRV_S, cluster = dat$Study_ID, r = 0.5)

mod_S5 <-rma.mv(yi = lnRR_Sa, V = VCV_S3a, mod = ~Age_stress_exposure-1, random = list(~1|Study_ID,
                                                                                       ~1|ES_ID,
                                                                                       ~1|Strain),
                test = "t",
                data = dat)
summary(mod_S5) 
r2_ml(mod_S5) 

# Orchard plot 
Age_S <- orchard_plot(mod_S5, mod = "Age_stress_exposure", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        text = element_text(size = 15), # change font sizes
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10)) 
```

#### Stess duration
How long was the stress applied for (chronic = every day for 7 days or more)?
This has the highest marginal R2

``` {r, message = FALSE, warning = FALSE}
dat4 <- filter(dat, Stress_duration %in% c("Chronic", "Acute"))
VCV_S4 <- impute_covariance_matrix(vi = dat4$lnRRV_S, cluster = dat$Study_ID, r = 0.5)

mod_S6 <-rma.mv(yi = lnRR_Sa, V = VCV_S4, mod = ~Stress_duration-1, random = list(~1|Study_ID,
                                                                                   ~1|ES_ID,
                                                                                   ~1|Strain),
                test = "t",
                data = dat4)
summary(mod_S6) 
r2_ml(mod_S6) 

# Orchard plot 
Duration_S <- orchard_plot(mod_S6, mod = "Stress_duration", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        text = element_text(size = 15), # change font sizes
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10)) 
```


### Full model
``` {r, message = FALSE, warning = FALSE}

# TODO - put the full model after uni-moderator models - so to match the text (and this will be more logical)

dat$Study_ID <-as.integer(dat$Study_ID)
#selecting moderator levels with k >=5
dat_Sfm <- dat %>%
  filter(Type_learning %in% c("Recognition", "Habituation", "Conditioning"),
         Appetitive_vs_aversive %in% c("Appetitive", "Aversive", "Not applicable"),
         Type_stress_exposure %in% c("Restraint", "Noise", "MS", "Combination"),
         Stress_duration %in% c("Chronic", "Acute"))

VCV_Sfm <- impute_covariance_matrix(vi = dat_Sfm$lnRRV_E, cluster = dat$Study_ID, r = 0.5)
                 
mod_Sfm <- rma.mv(yi = lnRR_Sa, V = VCV_Sfm, mod = ~ Type_learning -1 + Learning_vs_memory + Appetitive_vs_aversive + Type_stress_exposure + Age_stress_exposure + Stress_duration, random =   list(~1|Study_ID,
                                                                                    ~1|ES_ID,
                                                                                    ~1|Strain),
                    test = "t",
                 data = dat_Sfm)
summary(mod_Sfm)
r2_ml(mod_Sfm) 

res_Sfm <- dredge(mod_Sfm, trace=2)
res_Sfm2<- subset(res_Sfm, delta <= 6, recalc.weights=FALSE)
importance(res_Sfm2) #only consists of one model with delta <=2
```

### Publication bias & sensitivity analysis

``` {r, message = FALSE, warning = FALSE}

funnel(mod_Sfm)

#calculating inv effective sample size for use in full meta-regression
dat_Sfm$sqrt_inv_e_n <- with(dat_Sfm, sqrt(1/CC_n + 1/EC_n + 1/ES_n + 1/CS_n))

#time lag bias and eggers regression
dat_Sfm$c_Year_published <- as.vector(scale(dat_Sfm$Year_published, scale = F))

#TODO - should we do this for the full model or just put key moderators indentified by our analysis
# this is why it is good to have this at the end 
PB_MR_S<- rma.mv(lnRR_Sa, lnRRV_S, mods = ~1 + sqrt_inv_e_n +  c_Year_published + Type_learning + Appetitive_vs_aversive + Type_stress_exposure + Age_stress_exposure, random = list(~1|Study_ID,
                                                          ~1|ES_ID,
                                                          ~1|Strain), 
                 method = "REML", 
                 test = "t", 
                 data = dat_Sfm,
                  control=list(optimizer="optim", optmethod="Nelder-Mead"))

estimates_PB_MR_S<- estimates.CI(PB_MR_S)
estimates_PB_MR_S
#no effect of inv_effective sample size or year published

#leave-one-out analysis
dat$Study_ID <- as.factor(dat$Study_ID)

LeaveOneOut_effectsize <- list()
for(i in 1:length(levels(dat$Study_ID))){
  LeaveOneOut_effectsize[[i]] <- rma.mv(yi = lnRR_Sa, V = lnRRV_S, 
                                        random = list(~1 | Study_ID,~1| ES_ID, ~1 | Strain), 
                                        method = "REML", data = dat[dat$Study_ID
                                                                    != levels(dat$Study_ID)[i], ])}


# writing function for extracting est, ci.lb, and ci.ub from all models
est.func <- function(mod_E0){
  df <- data.frame(est = mod_E0$b, lower = mod_E0$ci.lb, upper = mod_E0$ci.ub)
  return(df)
}


#using dplyr to form data frame
MA_CVR <- lapply(LeaveOneOut_effectsize, function(x) est.func(x))%>% bind_rows %>% mutate(left_out = levels(dat$Study_ID))

#telling ggplot to stop reordering factors
MA_CVR$left_out<- as.factor(MA_CVR$left_out)
MA_CVR$left_out<-factor(MA_CVR$left_out, levels = MA_CVR$left_out)

#plotting
leaveoneout_S <- ggplot(MA_CVR) +
  geom_hline(yintercept = 0, lty = 2, lwd = 1) +
  geom_hline(yintercept = mod_S0$ci.lb, lty = 3, lwd = 0.75, colour = "black") +
  geom_hline(yintercept = mod_S0$b, lty = 1, lwd = 0.75, colour = "black") +
  geom_hline(yintercept = mod_S0$ci.ub, lty = 3, lwd = 0.75, colour = "black") +
  geom_pointrange(aes(x = left_out, y = est, ymin = lower, ymax = upper)) +
  xlab("Study left out") + 
  ylab("lnRR, 95% CI") + 
  coord_flip() +
  theme(panel.grid.minor = element_blank())+
  theme_bw() + theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor.x = element_blank() ) +
  theme(axis.text.y = element_text(size = 6))

leaveoneout_S

dat$Study_ID <- as.integer(dat$Study_ID)
```


## Interaction of stress and EE

### Intercept
Enriched and stress animals are better at learning and memory. 
Note: interaction is slightly non-significant after including Wang et al (study that we shifted up due to negative values)

``` {r, message = FALSE, warning = FALSE}
mod_ES0 <- rma.mv(yi = lnRR_ESa, V = VCV_ES, random = list(~1|Study_ID,
                                                             ~1|ES_ID,
                                                             ~1|Strain),
                  test = "t", 
                  data = dat)

summary(mod_ES0) 
i2_ml(mod_ES0) 

orchard_plot(mod_ES0, mod = "Int", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        text = element_text(size = 24), # change font sizes
        legend.title = element_text(size = 15),
        legend.text = element_text(size = 13)) 

#running the model again with the extreme outlier removed
dat_outliers <- dat %>%
  filter(ES_ID != 88)

VCV_ES_outliers <- impute_covariance_matrix(vi = dat_outliers$lnRRV_E, cluster = dat$Study_ID, r = 0.5)

mod_ESoutlier <- rma.mv(yi = lnRR_ESa, V = VCV_ES_outliers, random = list(~1|Study_ID,
                                                             ~1|ES_ID,
                                                             ~1|Strain),
                  test = "t", 
                  data = dat_outliers)

summary(mod_ES0)

orchard_plot(mod_ESoutlier, mod = "Int", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        text = element_text(size = 24), # change font sizes
        legend.title = element_text(size = 15),
        legend.text = element_text(size = 13))   
```

### Meta-regression

#### Type of learning
The type of learning/memory response 

``` {r, message = FALSE, warning = FALSE}
VCV_ES1 <- impute_covariance_matrix(vi = dat1$lnRRV_ES, cluster = dat$Study_ID, r = 0.5)

mod_ES1 <- rma.mv(yi = lnRR_ESa, V = VCV_ES1, mod = ~Type_learning-1, random = list(~1|Study_ID,
                                                                                    ~1|ES_ID,
                                                                                    ~1|Strain),
                  test = "t",
                  data = dat1)

summary(mod_ES1)
r2_ml(mod_ES1) 

# Orchard plot 
Learning_ES <- orchard_plot(mod_ES1, mod = "Type_learning", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  geom_point(aes(fill = name),  size = 3, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        axis.text.x = element_text(size = 10), # change font sizes
        axis.text.y = element_text(size = 10),
        legend.title = element_text(size = 7),
        legend.text = element_text(size = 7)) 
```

#### Learning vs Memory
Is the assay broadly measuring learning or memory? 

``` {r, message = FALSE, warning = FALSE}
mod_ES2 <-  rma.mv(yi = lnRR_ESa, V = VCV_ES, mod = ~Learning_vs_memory-1, random = list(~1|Study_ID, 
                                                                                           ~1|ES_ID,
                                                                                           ~1|Strain),
                   test = "t",
                   data = dat)

summary(mod_ES2) 
r2_ml(mod_ES2) 

# Orchard plot 
LvsM_ES <- orchard_plot(mod_ES2, mod = "Learning_vs_memory", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  geom_point(aes(fill = name),  size = 3, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        axis.text.x = element_text(size = 10), # change font sizes
        axis.text.y = element_text(size = 10),
        legend.title = element_text(size = 7),
        legend.text = element_text(size = 7)) 
```

#### Type of reinforcement
The type of conditioning used

``` {r, message = FALSE, warning = FALSE}
VCV_ES2 <- impute_covariance_matrix(vi = dat2$lnRRV_ES, cluster = dat2$Study_ID, r = 0.5)

mod_ES3 <- rma.mv(yi = lnRR_ESa, V = VCV_ES2, mod = ~ Appetitive_vs_aversive-1, random = list(~1|Study_ID,
                                                                                               ~1|ES_ID,
                                                                                               ~1|Strain),
                  test = "t",
                  data = dat2)

summary(mod_ES3)
r2_ml(mod_ES3) 

# Orchard plot 
Reinforcement_ES <- orchard_plot(mod_ES3, mod = "Appetitive_vs_aversive", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  geom_point(aes(fill = name),  size = 3, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        axis.text.x = element_text(size = 10), # change font sizes
        axis.text.y = element_text(size = 10),
        legend.title = element_text(size = 7),
        legend.text = element_text(size = 7)) 
````

#### Type of stress
The type of stress manipulation 

``` {r, message = FALSE, warning = FALSE}
VCV_ES3 <- impute_covariance_matrix(vi = dat3$lnRRV_ES, cluster = dat$Study_ID, r = 0.5)
mod_ES4 <- rma.mv(yi = lnRR_ESa, V = VCV_ES3, mod = ~Type_stress_exposure-1, random = list(~1|Study_ID,
                                                                                            ~1|ES_ID,
                                                                                            ~1|Strain),
                  test = "t",
                  data = dat3)
summary(mod_ES4)
r2_ml(mod_ES4)

# Orchard plot 
Stressor_ES <- orchard_plot(mod_ES4, mod = "Type_stress_exposure", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  geom_point(aes(fill = name),  size = 3, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        axis.text.x = element_text(size = 10), # change font sizes
        axis.text.y = element_text(size = 10),
        legend.title = element_text(size = 7),
        legend.text = element_text(size = 7))  
````

#### Age of stress
The age at which the individuals were exposed to the stressor.
``` {r, message = FALSE, warning = FALSE}
mod_ES5 <-rma.mv(yi = lnRR_ESa, V = VCV_ES, mod = ~Age_stress_exposure-1, random = list(~1|Study_ID,
                                                                                          ~1|ES_ID,
                                                                                          ~1|Strain),
                 test = "t",
                 data = dat)
summary(mod_ES5) 
r2_ml(mod_ES5) 

# Orchard plot 
Age_stress_ES<-orchard_plot(mod_ES5, mod = "Age_stress_exposure", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  geom_point(aes(fill = name),  size = 3, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
       axis.text.x = element_text(size = 10), # change font sizes
        axis.text.y = element_text(size = 10),
        legend.title = element_text(size = 7),
        legend.text = element_text(size = 7)) 
```

#### Stress duration
How long was the stress applied for (chronic = every day for 7 days or more)?
This has the highest marginal R2 (currentl nearly 43%) - need to redo without outlier

``` {r, message = FALSE, warning = FALSE}
VCV_ES4 <- impute_covariance_matrix(vi = dat4$lnRRV_ES, cluster = dat4$Study_ID, r = 0.5)

mod_ES6 <-rma.mv(yi = lnRR_ESa, V = VCV_ES4, mod = ~Stress_duration-1, random = list(~1|Study_ID,
                                                                                      ~1|ES_ID,
                                                                                      ~1|Strain),
                 test = "t",
                 data = dat4)
summary(mod_ES6) 
r2_ml(mod_ES6) 

# Orchard plot 
Duration_ES<- orchard_plot(mod_ES6, mod = "Stress_duration", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  geom_point(aes(fill = name),  size = 3, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        axis.text.x = element_text(size = 10), # change font sizes
        axis.text.y = element_text(size = 10),
        legend.title = element_text(size = 7),
        legend.text = element_text(size = 7)) 
```

#### Social enrichment
Does EE also include a manipulation of social environment (i.e., number of individuals in EE relative to control)? 

``` {r, message = FALSE, warning = FALSE}
VCV_ES5 <- impute_covariance_matrix(vi = dat5$lnRRV_ES, cluster = dat5$Study_ID, r = 0.5)
mod_ES7<- rma.mv(yi = lnRR_ESa, V = VCV_ES5, mod = ~EE_social-1, random = list(~1|Study_ID,
                                                                                ~1|ES_ID,
                                                                                ~1|Strain),
                 test = "t",
                 data = dat5)

summary(mod_ES7)
r2_ml(mod_ES7) 

# Orchard plot 
Social_ES <- orchard_plot(mod_ES7, mod = "EE_social", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  geom_point(aes(fill = name),  size = 3, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        axis.text.x = element_text(size = 10), # change font sizes
        axis.text.y = element_text(size = 10),
        legend.title = element_text(size = 7),
        legend.text = element_text(size = 7)) 
```

#### Exercise enrichment
Does the form of enrichment include exercise through a running wheel or treadmill? 

``` {r, message = FALSE, warning = FALSE}
mod_ES8<- rma.mv(yi = lnRR_ESa, V = VCV_ES, mod = ~EE_exercise-1, random = list(~1|Study_ID, 
    ~1|ES_ID,
    ~1|Strain),
     test = "t",
     data = dat)

summary(mod_ES8)
r2_ml(mod_ES8) 

# Orchard plot 
Exercise_ES <- orchard_plot(mod_ES8, mod = "EE_exercise", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  geom_point(aes(fill = name),  size = 3, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
       axis.text.x = element_text(size = 10), # change font sizes
        axis.text.y = element_text(size = 10),
        legend.title = element_text(size = 7),
        legend.text = element_text(size = 7)) 
```

#### Order to treatment exposure
What order were animals exposed to stress and EE

``` {r, message = FALSE, warning = FALSE}
mod_ES9 <- rma.mv(yi = lnRR_ESa, V = VCV_ES, mod = ~Stress_vs_EE_timing -1, random = list(~1|Study_ID, 
    ~1|ES_ID,
    ~1|Strain),
     test = "t",
     data = dat)

summary(mod_ES9)
r2_ml(mod_ES9)

Order_ES <- orchard_plot(mod_ES9, mod = "Stress_vs_EE_timing", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  geom_point(aes(fill = name),  size = 3, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        axis.text.x = element_text(size = 10), # change font sizes
        axis.text.y = element_text(size = 10),
        legend.title = element_text(size = 7),
        legend.text = element_text(size = 7)) 

```

### Age of enrichment
What age were individuals exposed to EE
``` {r, message = FALSE, warning = FALSE}
VCV_ES6 <- impute_covariance_matrix(vi = dat6$lnRRV_ES, cluster = dat6$Study_ID, r = 0.5)

mod_ES10 <- rma.mv(yi = lnRR_ESa, V = VCV_ES6, mod = ~Age_EE_exposure-1, random = list(~1|Study_ID,
                                                                                    ~1|ES_ID,
                                                                                    ~1|Strain),
                 test = "t",
                 data = dat6)

summary(mod_ES10) 
r2_ml(mod_ES10) 

#Orchard plot 
Age_enrichment_ES <- orchard_plot(mod_ES10, mod = "Age_EE_exposure", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  geom_point(aes(fill = name),  size = 3, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
       axis.text.x = element_text(size = 10), # change font sizes
        axis.text.y = element_text(size = 10),
        legend.title = element_text(size = 7),
        legend.text = element_text(size = 7)) 


```


### Full model
``` {r, message = FALSE, warning = FALSE}
dat_ESfm <- dat %>%
  filter(Type_learning %in% c("Recognition", "Habituation", "Conditioning"),
         Appetitive_vs_aversive %in% c("Appetitive", "Aversive", "Not applicable"),
         EE_social %in% c("Social", "Non-social"),
         Age_EE_exposure %in% c("Adult", "Adolescent"),
         Type_stress_exposure %in% c("Restraint", "Noise", "MS", "Combination"),
         Stress_duration %in% c("Chronic", "Acute"), 
         Age_stress_exposure %in% c("Prenatal", "Early postnatal", "Adult"))

VCV_ESfm <- impute_covariance_matrix(vi = dat_ESfm$lnRRV_ES, cluster = dat$Study_ID, r = 0.5)
                 
mod_ESfm <- rma.mv(yi = lnRR_Sa, V = VCV_ESfm, mod = ~Type_learning-1 + Learning_vs_memory-1 + Appetitive_vs_aversive-1 + EE_social-1 + EE_exercise-1 + Age_EE_exposure-1 + Type_stress_exposure-1 + Age_stress_exposure-1 + Stress_duration-1 + Stress_vs_EE_timing, random =   list(~1|Study_ID,
                                                                                    ~1|ES_ID,
                                                                                    ~1|Strain),
                    test = "t",
                 data = dat_ESfm)
summary(mod_ESfm)
r2_ml(mod_ESfm) 


res_ESfm <- dredge(mod_ESfm, trace=2)
res_ESfm2<- subset(res_ESfm, delta <= 6, recalc.weights=FALSE)
importance(res_ESfm2) 
```

### Publication bias & sensitivity analysis
``` {r, message = FALSE, warning = FALSE}
funnel(mod_ESfm)

#year published was scaled previously under stress PB

dat_ESfm$sqrt_inv_e_n <- with(dat_ESfm, sqrt(1/CC_n + 1/EC_n + 1/ES_n + 1/CS_n))

PB_MR_ES<- rma.mv(lnRR_ESa, lnRRV_ES, mods = ~1 + sqrt_inv_e_n +  Year_published + Type_learning + Appetitive_vs_aversive + EE_social + EE_exercise + Age_stress_exposure, random = list(~1|Study_ID,
                                                          ~1|ES_ID,
                                                          ~1|Strain), method = "REML", test = "t", 
    data = dat_ESfm)

estimates_PB_MR_ES<- estimates.CI(PB_MR_ES)
estimates_PB_MR_ES

#no effect of inv_effective sample size or year published

#leave-one-out analysis
dat$Study_ID <- as.factor(dat$Study_ID)

LeaveOneOut_effectsize <- list()
for(i in 1:length(levels(dat$Study_ID))){
  LeaveOneOut_effectsize[[i]] <- rma.mv(yi = lnRR_Ea, V = lnRRV_E, 
                                        random = list(~1 | Study_ID,~1| ES_ID, ~1 | Strain), 
                                        method = "REML", data = dat[dat$Study_ID
                                                                    != levels(dat$Study_ID)[i], ])}


# writing function for extracting est, ci.lb, and ci.ub from all models
est.func <- function(mod_E0){
  df <- data.frame(est = mod_E0$b, lower = mod_E0$ci.lb, upper = mod_E0$ci.ub)
  return(df)
}


#using dplyr to form data frame
MA_CVR <- lapply(LeaveOneOut_effectsize, function(x) est.func(x))%>% bind_rows %>% mutate(left_out = levels(dat$Study_ID))

#telling ggplot to stop reordering factors
MA_CVR$left_out<- as.factor(MA_CVR$left_out)
MA_CVR$left_out<-factor(MA_CVR$left_out, levels = MA_CVR$left_out)

#plotting
leaveoneout_ES <- ggplot(MA_CVR) +
  geom_hline(yintercept = 0, lty = 2, lwd = 1) +
  geom_hline(yintercept = mod_E0$ci.lb, lty = 3, lwd = 0.75, colour = "black") +
  geom_hline(yintercept = mod_E0$b, lty = 1, lwd = 0.75, colour = "black") +
  geom_hline(yintercept = mod_E0$ci.ub, lty = 3, lwd = 0.75, colour = "black") +
  geom_pointrange(aes(x = left_out, y = est, ymin = lower, ymax = upper)) +
  xlab("Study left out") + 
  ylab("lnRR, 95% CI") + 
  coord_flip() +
  theme(panel.grid.minor = element_blank())+
  theme_bw() + theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor.x = element_blank() ) +
  theme(axis.text.y = element_text(size = 6))

leaveoneout_ES

dat$Study_ID <- as.integer(dat$Study_ID)
```

## Combined orchard plot

``` {r, message = FALSE, warning = FALSE}
mod_list1 <- list(mod_E0, mod_S0, mod_ES0)

mod_res1 <- lapply(mod_list1, function(x) mod_results(x, mod = "Int"))

merged1 <- submerge(mod_res1[[3]], mod_res1[[2]],  mod_res1[[1]], mix = T)
merged1$mod_table$name <- factor(merged1$mod_table$name, levels = c("Intrcpt1", 
    "Intrcpt2", "Intrcpt3"), 
    labels = rev(c("Enrichment ME", "Stress ME", "Interaction")))

merged1$data$moderator <- factor(merged1$data$moderator, levels = c("Intrcpt1", 
    "Intrcpt2", "Intrcpt3"), 
    labels = rev(c("Enrichment ME", "Stress ME", "Interaction")))

orchard1<- orchard_plot(merged1, mod = "Int", xlab = "lnRR", angle = 0) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals 
  xlim(-2,4.5) +
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        text = element_text(size = 15), # change font sizes
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10)) 

orchard1
```

#### Age of enrichment
The age at which the individuals were exposed to environmental enrichment.  
This needs to be redone after recategorising
``` {r, message = FALSE, warning = FALSE}
mod_ES9 <- rma.mv(yi = lnRR_ESa, V = lnRRV_ES, mod = ~Age_EE_exposure-1, random = list(~1|Study_ID,
                                                                                       ~1|ES_ID,
                                                                                       ~1|Strain),
                  test = "t",
                  data = dat)

summary(mod_ES9) 
r2_ml(mod_ES9) 


# Orchard plot 
orchard_plot(mod_ES9, mod = "Age_EE_exposure", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        text = element_text(size = 24), # change font sizes
        legend.title = element_text(size = 15),
        legend.text = element_text(size = 13)) 
```

# 'Pairwise effect sizes'
Comparing ES relative to stress we can see that the increase is about 18% but ES relative to control is 12% (i.e., this is the interaction). 

We can also see that ES relative to control 9% so these individuals actually do better than baseline individuals. There is also no significant difference between ES and EC individuals (although estimate is slightly lower), meaning that enrichment in the presence of stress can result in learning and memory that is just as good as enriched individuals without stress

## Enrichment relative to control

``` {r, message = FALSE, warning = FALSE}

VCV_E20 <- impute_covariance_matrix(vi = dat$lnRRV_E2, cluster = dat$Study_ID, r = 0.5)

#Model doesn't converge with VCV
mod_E20 <- rma.mv(yi = lnRR_E2a, V = VCV_E20, random = list(~1|Study_ID,
                                                             ~ 1|Strain,
                                                             ~1|ES_ID),
                 test = "t", 
                 data = dat, 
                 control=list(optimizer="optim", optmethod="Nelder-Mead"))

summary(mod_E20) 
i2_ml(mod_E20) 

orchard_plot(mod_E20, mod = "Int", xlab = "lnRR")
```

## Stress relative to control

``` {r, message = FALSE, warning = FALSE}
VCV_S20 <- impute_covariance_matrix(vi = dat$lnRRV_S2, cluster = dat$Study_ID, r = 0.5)

mod_S20 <- rma.mv(yi = lnRR_S2a, V = VCV_S20, random = list(~1|Study_ID, 
                                                             ~ 1|Strain,
                                                             ~1|ES_ID),
                 test = "t",
                 data = dat)

summary(mod_S20) 
i2_ml(mod_S20) 
 
orchard_plot(mod_S20, mod = "Int", xlab = "lnRR")
```

## Enrichment + stress relative to control

``` {r, message = FALSE, warning = FALSE}
VCV_ES20 <- impute_covariance_matrix(vi = dat$lnRRV_ES2, cluster = dat$Study_ID, r = 0.5)

mod_ES20 <- rma.mv(yi = lnRR_ES2a, V = VCV_ES20, random = list(~1|Study_ID,
                                                                ~ 1|Strain,
                                                                ~1|ES_ID),
                 test = "t",
                 data = dat)
summary(mod_ES20) 
i2_ml(mod_ES20) 

orchard_plot(mod_ES20, mod = "Int", xlab = "lnRR")
```

## Enrichment + stress relative to stress

``` {r, message = FALSE, warning = FALSE}
VCV_E30 <- impute_covariance_matrix(vi = dat$lnRRV_E3, cluster = dat$Study_ID, r = 0.5)

mod_E30 <- rma.mv(yi = lnRR_E3a, V = VCV_E30, random = list(~1|Study_ID,
                                                             ~ 1|Strain,
                                                             ~1|ES_ID),
                  test = "t",
                  data = dat)
summary(mod_E30) 
i2_ml(mod_E30) 

orchard_plot(mod_E30, mod = "Int", xlab = "lnRR")
```

## Enrichment + stress relative to enrichment

``` {r, message = FALSE, warning = FALSE}
VCV_S30 <- impute_covariance_matrix(vi = dat$lnRRV_S3, cluster = dat$Study_ID, r = 0.5)

mod_S30 <- rma.mv(yi = lnRR_S3a, V = VCV_S30, random = list(~1|Study_ID,
                                                             ~ 1|Strain,
                                                             ~1|ES_ID),
                  test = "t",
                  data = dat,
                   control=list(optimizer="optim", optmethod="Nelder-Mead"))
summary(mod_S30) 
i2_ml(mod_S30) 

orchard_plot(mod_S30, mod = "Int", xlab = "lnRR")
```

## Combined orchard plot
``` {r, message = FALSE, warning = FALSE}

mod_list2 <- list(mod_S30, mod_E30, mod_ES20, mod_S20, mod_E20) #rearranged the order so that it matches intext results

mod_res2 <- lapply(mod_list2, function(x) mod_results(x, mod = "Int"))

merged2 <- submerge(mod_res2[[1]], mod_res2[[2]],  mod_res2[[3]], mod_res2[[4]],  mod_res2[[5]], mix = T)

merged2$mod_table$name <- factor(merged2$mod_table$name, levels = c("Intrcpt1", 
    "Intrcpt2", "Intrcpt3", "Intrcpt4", "Intrcpt5"), 
    labels = rev(c("EC/CC", "CS/CC", "ES/CC", "ES/CS", "ES/EC")))

merged2$data$moderator <- factor(merged2$data$moderator, levels = c("Intrcpt1", 
    "Intrcpt2", "Intrcpt3", "Intrcpt4", "Intrcpt5"), 
    labels = rev(c("EC/CC", "CS/CC", "ES/CC", "ES/CS", "ES/EC")))

orchard2 <- orchard_plot(merged2, mod = "Int", xlab = "lnRR", angle = 0) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals 
  xlim(-2,4.5) +
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        text = element_text(size = 15), # change font sizes
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10)) 

orchard2

```
## Panel of both orchard plots
``` {r, message = FALSE, warning = FALSE}
p1 <- orchard1 + orchard2 +  plot_annotation(tag_levels = 'A')
p1
```

##Panel of metagressions
``` {r, message = FALSE, warning = FALSE}
#Enrichment
E_mod <- (LvsM_E + Learning_E + Reinforcement_E)/ (Age_E + Exercise_E + Social_E) +  plot_annotation(tag_levels = 'A')

S_mod <- (LvsM_S + Learning_S + Reinforcement_S) / (Age_S + Stressor + Duration_S) + plot_annotation(tag_levels = 'A')

ES_mod <- plot_grid(LvsM_ES, Learning_ES, Reinforcement_ES, Age_enrichment_ES, Age_stress_ES, Order_ES, Exercise_ES, Social_ES, Stressor_ES, Duration_ES,
  labels = "AUTO", ncol = 5)

```

# Modelling with SMD

## Stress

### Intercept model
Why does the funnel plot look so strange and why is I2 higher?
``` {r, message = FALSE, warning = FALSE}
mod_S0a <- rma.mv(yi = SMD_Sa, V = VCV_Sa, random = list(~1|Study_ID,
                                                         ~1|ES_ID,
                                                         ~1|Strain),
                test = "t",
                data = dat)
summary(mod_S0a) 
i2_ml(mod_S0a) 
funnel(mod_S0a) 

funnel(mod_S0a, yaxis="seinv",) 


```

### Environmental Enrichment

#### Intercept model
Why does the funnel plot look so strange and why is I2 higher?
``` {r, message = FALSE, warning = FALSE}
mod_E0a <- rma.mv(yi = SMD_Ea, V = VCV_Ea, random = list(~1|Study_ID,
                                                         ~1|ES_ID, 
                                                         ~1|Strain),
                 test = "t",
                 data = dat)
summary(mod_E0a)
i2_ml(mod_E0a)
funnel(mod_E0a) 
```

### Interaction

#### Intercept model
Why does the funnel plot look so strange and why is I2 higher?
``` {r, message = FALSE, warning = FALSE}
mod_ES0a <- rma.mv(yi = SMD_ESa, V = VCV_ESa, random = list(~1|Study_ID,
                                                            ~1|ES_ID,
                                                            ~1|Strain),
                  test = "t",
                  data = dat)
summary(mod_ES0a)
i2_ml(mod_ES0a) #I2 is very high! 99.37%
funnel(mod_ES0a)
```
