---
title: "Dataset_summary"
authors: "Erin L Macartney, Malgorzata Lagisz, Shinichi Nakagawa"
date: "12/08/2021"
output:
  html_document:
    code_folding: hide
    df_print: kable
    toc: TRUE
    toc_float: TRUE
    toc_depth: 4
    collapsed: FALSE
    YAML: rmdformats::robobook
---

```{r setup, results = 'hide'}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

pacman::p_load(tidyverse, 
               here,
               readxl,
               metafor,
               emmeans,
               orchaRd, 
               corpcor,
               naniar,
               GoodmanKruskal,
               networkD3,
               ggplot2,
               ggalluvial,
               ggthemr,
               patchwork)

# Load custom function to extract data 
#source(here("R/functions.R")) 
source(here("R/functions_cleanedup.R")) 
```

#### Loading data and functions   
- Using "Full_data_ML2.xlsx" file

```{r load data, results = 'hide'}
dat <- read_excel(here("Data", "Full_data_ML3.xlsx"), sheet = 1)
dim(dat) #96 75
names(dat)
```

### Data organisation   
 - Calculating effect size
 - 'flipping' effect sizes so that all effect sizes are higher values = individuals do better and learning/memory
 - shifting negative values to positive as lnRR cannot use negative values.

```{r effect sizes, results = 'hide'}
#vis_miss(dat) #mostly data is missing at comment fields

#removing one study with negative mean values as these are unable to be used for lnRR
dat <- droplevels(dat[!dat$First_author == 'Wang',])
dim(dat) #92 75

#Getting effect sizes
effect_size <- effect_set(CC_n = "CC_n", CC_mean = "CC_mean", CC_SD = "CC_SD",
                          EC_n = "EC_n", EC_mean = "EC_mean" , EC_SD ="EC_SD",
                          CS_n = "CS_n", CS_mean = "CS_mean", CS_SD = "CS_SD",
                          ES_n = "ES_n", ES_mean = "ES_mean", ES_SD = "ES_SD",
                          data = dat)
#'pure' effect sizes
effect_size2 <- effect_set2(CC_n = "CC_n", CC_mean = "CC_mean", CC_SD = "CC_SD",
                          EC_n = "EC_n", EC_mean = "EC_mean" , EC_SD ="EC_SD",
                          CS_n = "CS_n", CS_mean = "CS_mean", CS_SD = "CS_SD",
                          ES_n = "ES_n", ES_mean = "ES_mean", ES_SD = "ES_SD",
                          data = dat) 

vis_miss(effect_size) +
  theme(plot.title = element_text(hjust = 0.5, vjust = 3), 
        plot.margin = margin(t = 0.5, r = 2, b = 1, l = 1, unit = "cm")) +
  ggtitle("Missing data in the first set of ES") #no mising values

vis_miss(effect_size2) +
  theme(plot.title = element_text(hjust = 0.5, vjust = 3), 
        plot.margin = margin(t = 0.5, r = 2, b = 1, l = 1, unit = "cm")) +
  ggtitle("Missing data in the second set of ES") #no mising values #no missing values

#Removing missing effect sizes
#full_info <- which(complete.cases(effect_size) == TRUE)
dat_effect <- cbind(dat, effect_size, effect_size2)
#dat <- dat_effect[full_info, ]
names(dat_effect)
#dat <- dat_effect[full_info, ]

dim(dat_effect) #92 97

#Flipping 'lower is better' effect sizes ############################ rewrite using https://dplyr.tidyverse.org/reference/if_else.html and try https://datacornering.com/use-ifelse-across-a-range-of-r-data-frame-columns/

#flipping lnRR for values where higher = worse
dat_effect$lnRR_Ea <- ifelse(dat_effect$Response_direction == 2, dat_effect$lnRR_E*-1, ifelse(is.na(dat_effect$Response_direction) == TRUE, NA, dat_effect$lnRR_E)) 
dat_effect$lnRR_Sa  <- ifelse(dat_effect$Response_direction == 2, dat_effect$lnRR_S*-1, ifelse(is.na(dat_effect$Response_direction) == TRUE, NA, dat_effect$lnRR_S)) 
dat_effect$lnRR_ESa <-  ifelse(dat_effect$Response_direction == 2, dat_effect$lnRR_ES*-1, ifelse(is.na(dat_effect$Response_direction) == TRUE, NA, dat_effect$lnRR_ES)) 

#flipping 'pure effect sizes'
dat_effect$lnRR_E2a <- ifelse(dat_effect$Response_direction == 2, dat_effect$lnRR_E2*-1, ifelse(is.na(dat_effect$Response_direction) == TRUE, NA, dat_effect$lnRR_E2)) 
dat_effect$lnRR_S2a  <- ifelse(dat_effect$Response_direction == 2, dat_effect$lnRR_S2*-1, ifelse(is.na(dat_effect$Response_direction) == TRUE, NA, dat_effect$lnRR_S2)) 
dat_effect$lnRR_ES2a <-  ifelse(dat_effect$Response_direction == 2, dat_effect$lnRR_ES2*-1, ifelse(is.na(dat_effect$Response_direction) == TRUE, NA, dat_effect$lnRR_ES2)) 
dat_effect$lnRR_E3a <-  ifelse(dat_effect$Response_direction == 2, dat_effect$lnRR_E3*-1, ifelse(is.na(dat_effect$Response_direction) == TRUE, NA, dat_effect$lnRR_E3)) 
dat_effect$lnRR_S3a <-  ifelse(dat_effect$Response_direction == 2, dat_effect$lnRR_S3*-1, ifelse(is.na(dat_effect$Response_direction) == TRUE, NA, dat_effect$lnRR_S3)) 

#flipping SMD
dat_effect$SMD_Ea <- ifelse(dat_effect$Response_direction == 2, dat_effect$SMD_E*-1,ifelse(is.na(dat_effect$Response_direction) == TRUE, NA, dat_effect$SMD_E)) 
dat_effect$SMD_Sa  <- ifelse(dat_effect$Response_direction == 2, dat_effect$SMD_S*-1,ifelse(is.na(dat_effect$Response_direction) == TRUE, NA, dat_effect$SMD_S)) 
dat_effect$SMD_ESa <-  ifelse(dat_effect$Response_direction == 2, dat_effect$SMD_ES*-1,ifelse(is.na(dat_effect$Response_direction) == TRUE, NA, dat_effect$SMD_ES))

#rounding down integer sample sizes 
dat_effect$CC_n <- floor(dat_effect$CC_n)
dat_effect$EC_n <- floor(dat_effect$EC_n)
dat_effect$CS_n <- floor(dat_effect$CS_n)
dat_effect$ES_n <- floor(dat_effect$CS_n)

names(dat_effect)

#remove columns ending or starting with certain words (these comment columnswill not be used in analyses)
dat_effect2 <- dat_effect %>% select(!matches("(_SE|centile|_median|_details|_comments|_notes|_author|_contacted|_response)$|^Notes_")) 
names(dat_effect2)

#vis_miss(dat_effect2) #see columns with missing values
```


### Assign human readable words to categorical moderators   
- These variables are stored as new columns (_HR)    
- Only using "revised" "Age" columns (info on life stages)   

```{r add human readable codes, results = 'hide'}
dat_effect2 <- dat_effect2 %>% mutate(Sex_HR = case_when(Sex == 1 ~ "Female",
                                                Sex == 2 ~ "Male",
                                                Sex == 3 ~ "Both sexes", 
                                                Sex == 4 ~ "Unclear"),
                                      Type_learning_HR = case_when(Type_learning == 1 ~ "Habituation",
                                                Type_learning == 2 ~ "Conditioning",
                                                Type_learning == 3 ~ "Recognition", 
                                                Type_learning == 4 ~ "Unclear"),
                      Learning_vs_memory_HR = case_when(Learning_vs_memory == 1 ~ "Learning",
                                                     Learning_vs_memory == 2 ~ "Memory", 
                                                     Learning_vs_memory == 3 ~ "Habituation"),
                      Appetitive_vs_aversive_HR = case_when(Appetitive_vs_aversive == 1 ~"Appetitive",
                                                         Appetitive_vs_aversive == 2 ~ "Aversive",
                                                         Appetitive_vs_aversive == 3 ~ "Not applicable",
                                                         Appetitive_vs_aversive == 4 ~ "Unclear"),
                      Type_stress_exposure_HR = case_when(Type_stress_exposure == 1 ~ "Density",
                                                       Type_stress_exposure == 2 ~ "Scent",
                                                       Type_stress_exposure == 3 ~ "Shock",
                                                       Type_stress_exposure == 4 ~ "Exertion",
                                                       Type_stress_exposure == 5 ~ "Restraint",
                                                       Type_stress_exposure == 6 ~ "Maternal Separation",
                                                       Type_stress_exposure == 7 ~ "Circadian rhythm",
                                                       Type_stress_exposure == 8 ~ "Noise",
                                                       Type_stress_exposure == 9 ~ "Other",
                                                       Type_stress_exposure == 10 ~ "Combination",
                                                       Type_stress_exposure == 11 ~ "unclear"), 
                      Age_stress_exposure_HR = case_when(Age_stress_revised == 1 ~ "Prenatal",
                                                      Age_stress_revised == 2 ~ "Early postnatal",
                                                      Age_stress_revised == 3 ~ "Adolescent",
                                                      Age_stress_revised == 4 ~ "Adult",
                                                      Age_stress_revised == 5 ~ "Unclear"),
                      Stress_duration_HR = case_when(Stress_duration == 1 ~ "Acute",
                                                  Stress_duration == 2 ~ "Chronic",
                                                  Stress_duration == 3 ~ "Intermittent",
                                                  Stress_duration == 4 ~ "Unclear"),
                      EE_social_HR = case_when(EE_social == 1 ~ "Social",
                                            EE_social== 2 ~ "Non-social", 
                                            EE_social == 3 ~ "Unclear"), 
                      EE_exercise_HR = case_when(EE_exercise == 1 ~ "Exercise", 
                                              EE_exercise == 2 ~ "No exercise"),
                      Age_EE_exposure_HR = case_when(Age_EE_revised == 1 ~ "Prenatal", 
                                                  Age_EE_revised == 2 ~ "Early postnatal",
                                                  Age_EE_revised == 3 ~ "Adolescent", 
                                                  Age_EE_revised == 4 ~ "Adult",
                                                  Age_EE_revised == 5 ~ "Unclear"),
                      Stress_vs_EE_timing_HR = case_when(Stress_vs_EE_timing == 1 ~ "Stress first",
                                                      Stress_vs_EE_timing == 2 ~ "Enrichment first",
                                                      Stress_vs_EE_timing == 3 ~ "Concurrently", 
                                                      Stress_vs_EE_timing == 4 ~ "Unclear"),
                      Age_assay_HR = case_when(Age_assay_revised == 1 ~ "Early postnatal", 
                                                  Age_assay_revised == 2 ~ "Adolescent", 
                                                  Age_assay_revised == 3 ~ "Adult",
                                                  Age_assay_revised == 4 ~ "Unclear"),
                      Type_EE_exposure_HR = case_when(Type_EE_exposure == 1 ~ "Nesting material",
                                                      Type_EE_exposure == 2 ~ "Objects",
                                                      Type_EE_exposure == 3 ~ "Cage complexity", 
                                                      Type_EE_exposure == 4 ~ "Wheel/trademill",
                                                      Type_EE_exposure == 5 ~ "Combination",
                                                      Type_EE_exposure == 6 ~ "Other", 
                                                      Type_EE_exposure == 7 ~ "Unclear"))

### Added: #Type_EE_exposure : 1 = nesting material, 2 = objects, 3 = complexity of cage (i.e., multilevel cages), 4 = wheel/treadmill, 5 = combination, 6 = other, 7 = unclear #Sex: 1 = female, 2 = male, 3 = mixed, 4= not clear
```

### General  

- Number of effect sizes: `r length(unique(dat_effect2$ES_ID))`  
- Number of studies: `r length(dat_effect2$Study_ID)`  
- Publication years: from `r min(dat_effect2$Year_published)` to `r max(dat_effect2$Year_published)`    


### Explore associations among predictor variables   

```{r exploratory plots, results = 'hide'}

#see columns with missing values
vis_miss(dat_effect2) +
  theme(plot.title = element_text(hjust = 0.5, vjust = 3), 
        plot.margin = margin(t = 0.5, r = 3, b = 1, l = 1, unit = "cm")) +
  ggtitle("Missing data in the selected predictors") #no mising values

dim(dat_effect2)
#names(dat_effect2)
#str(dat_effect2)

#useGoodman and Kruskal’s τ measure of association between categorical predictor variables (function from package GoodmanKruskal: https://cran.r-project.org/web/packages/GoodmanKruskal/vignettes/GoodmanKruskal.html)
GKmatrix <- GKtauDataframe(subset(dat_effect2, select = c("Strain", "Sex", "Housing", "Age_EE_revised", "Age_stress_revised", "Age_assay_revised", "Type_EE_exposure", "EE_exercise", "EE_social", "Type_stress_exposure", "Stress_duration", "Stress_vs_EE_timing", "Learning_vs_memory",  "Type_learning", "Appetitive_vs_aversive")) )
plot(GKmatrix)
#as above using human-readable (HR) variables only
GKmatrix <- GKtauDataframe(subset(dat_effect2, select = c("Sex_HR", "Type_learning_HR", "Learning_vs_memory_HR", "Appetitive_vs_aversive_HR",  "Type_stress_exposure_HR", "Age_stress_exposure_HR", "Stress_duration_HR", "EE_social_HR", "EE_exercise_HR", "Age_EE_exposure_HR", "Stress_vs_EE_timing_HR", "Age_assay_HR")) )
plot(GKmatrix)

#simple pairwise contingency tables
table(dat_effect2$Type_learning_HR, dat_effect2$Appetitive_vs_aversive_HR) #some cleanup needed!
table(dat_effect2$Age_stress_exposure_HR, dat_effect2$Age_EE_exposure_HR) #check "unclear" for Age_EE_exposure_HR
table(dat_effect2$Type_stress_exposure_HR, dat_effect2$Age_stress_exposure_HR)
table(dat_effect2$Type_stress_exposure_HR, dat_effect2$Age_assay_HR)
table(dat_effect2$Type_stress_exposure_HR, dat_effect2$Stress_duration_HR)
```

There are associations among:   
 - Type_learning_HR, Appetitive_vs_aversive_HR (some cleanup needed)   
 - Age_stress_exposure_HR, Age_EE_exposure_HR (check "unclear" for Age_EE_exposure_HR)   
 - Type_stress_exposure_HR, Age_stress_exposure_HR   
 - Type_stress_exposure_HR, Age_assay_HR   
 - Type_stress_exposure_HR, Stress_duration_HR  

### Alluvial diagrams for species, strain and sex variables   

```{r alluvial plots species strains sex, results = 'hide'}

# create a frequency table for Species and Strain variables
freq_1 <- as.data.frame(table(dat_effect2$Common_species, dat_effect2$Strain)) %>% rename(Species = Var1, Strain = Var2)
#use ggalluvial (https://cran.r-project.org/web/packages/ggalluvial/vignettes/ggalluvial.html)
is_alluvia_form(as.data.frame(freq_1), axes = 1:2, silent = TRUE)

ggplot(data = freq_1,
  aes(axis1 = Species, axis2 = Strain, y = Freq)) +
  geom_alluvium(aes(fill = Strain)) +
  geom_stratum(aes(fill = Species)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
#theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Species", "Strain"), expand = c(0.15, 0.05), position = "top") +
  ggtitle("Species and strains used (set1)")


# create frequency table for Sex, Species and Strain

freq_2 <- as.data.frame(table(dat_effect2$Sex_HR, dat_effect2$Common_species, dat_effect2$Strain)) %>% rename(Sex = Var1, Species = Var2, Strain = Var3)
is_alluvia_form(as.data.frame(freq_2), axes = 1:3, silent = TRUE)

ggplot(data = freq_2,
  aes(axis1 = Sex, axis2 = Species, axis3 = Strain, y = Freq)) +
  geom_alluvium(aes(fill = Sex)) +
  geom_flow() +
  geom_stratum(aes(fill = Sex)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  #theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Sex", "Species", "Strain"), expand = c(0.15, 0.05), position = "top") +
  ggtitle("Species, strains and sex used (set2)")

freq_2 %>% filter(Freq != 0) %>% arrange(desc(Freq)) #collapesd table of values, without 0s

```


### Alluvial diagrams for Age (life stages) variables   

```{r alluvial plots age, results = 'hide'}

# create frequency table for 2 categorical Age variables
freq_ages1 <- as.data.frame(table(dat_effect2$Age_stress_exposure_HR, dat_effect2$Age_EE_exposure_HR)) %>% rename(Age_stress = Var1, Age_EE = Var2)
is_alluvia_form(as.data.frame(freq_ages1), axes = 1:2, silent = TRUE)

ggplot(data = freq_ages1,
  aes(axis1 = Age_stress, axis2 = Age_EE, y = Freq)) +
  geom_alluvium(aes(fill = Age_EE)) +
  geom_stratum(aes(fill = Age_stress)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
#theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Stress", "Enrichment"), expand = c(0.15, 0.05), position = "top") +
  ggtitle("Life stages used (set1)")


# create frequency table for 3 categorical Age variables

freq_ages2 <- as.data.frame(table(dat_effect2$Age_stress_exposure_HR, dat_effect2$Age_EE_exposure_HR, dat_effect2$Age_assay_HR)) %>% rename(Age_stress = Var1, Age_EE = Var2, Age_assay = Var3)

#use ggalluvial (https://cran.r-project.org/web/packages/ggalluvial/vignettes/ggalluvial.html)
is_alluvia_form(as.data.frame(freq_ages2), axes = 1:3, silent = TRUE)

ggplot(data = freq_ages2,
  aes(axis1 = Age_stress, axis2 = Age_EE, axis3 = Age_assay, y = Freq)) +
  geom_alluvium(aes(fill = Age_stress)) +
  geom_flow() +
  geom_stratum(aes(fill = Age_stress)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  #theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Stress", "Enrichment", "Assay"), expand = c(0.15, 0.05), position = "top") +
  ggtitle("Life stages used (set2)")

freq_ages2 %>% filter(Freq != 0) %>% arrange(desc(Freq)) #collapesd table of values, without 0s

# create frequency table for 3 categorical Age variables

freq_ages3 <- as.data.frame(table(dat_effect2$Age_stress_exposure_HR, dat_effect2$Age_EE_exposure_HR, dat_effect2$Age_assay_HR, dat_effect2$Stress_vs_EE_timing_HR)) %>% rename(Age_stress = Var1, Age_EE = Var2, Age_assay = Var3, Order = Var4)
is_alluvia_form(as.data.frame(freq_ages3), axes = 1:4, silent = TRUE)

ggplot(data = freq_ages3,
  aes(axis1 = Age_stress, axis2 = Age_EE, axis3 = Age_assay, axis4 = Order,  y = Freq)) +
  geom_alluvium(aes(fill = Age_stress)) +
  geom_flow() +
  geom_stratum(aes(fill = Age_stress)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  #theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Stress", "Enrichment", "Assay", "Order"), expand = c(0.15, 0.05), position = "top") +
  ggtitle("Life stages used and order (set3)")

freq_ages2 %>% filter(Freq != 0) %>% arrange(desc(Freq)) #collapesd table of values, without 0s
freq_ages3 %>% filter(Freq != 0) %>% arrange(desc(Freq)) #collapesd table of values, without 0s

```


### Alluvial diagrams for Stress variables

```{r alluvial plots stress, results = 'hide'}

# create frequency table for 2 categorical Stress variables
freq_stress1 <- as.data.frame(table(dat_effect2$Stress_duration_HR, dat_effect2$Type_stress_exposure_HR)) %>% rename(Stress_duration = Var1,  Stress_type = Var2)
is_alluvia_form(as.data.frame(freq_stress1), axes = 1:2, silent = TRUE)

ggplot(data = freq_stress1,
  aes(axis1 = Stress_duration, axis2 = Stress_type, y = Freq)) +
  geom_alluvium(aes(fill = Stress_duration)) +
  geom_stratum(aes(fill = Stress_duration)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
#theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Duration", "Type"), expand = c(0.15, 0.05), position = "top") +
  ggtitle("Stress exposure  variables (set1)")

# create frequency table for 3 categorical Stress variables
freq_stress2 <- as.data.frame(table(dat_effect2$Age_stress_exposure_HR, dat_effect2$Stress_duration_HR, dat_effect2$Type_stress_exposure_HR)) %>% rename(Age_stress = Var1, Duration_stress = Var2, Type_stress = Var3)
is_alluvia_form(as.data.frame(freq_stress2), axes = 1:3, silent = TRUE)

ggplot(data = freq_stress2,
  aes(axis1 = Age_stress, axis2 = Duration_stress, axis3 = Type_stress, y = Freq)) +
  geom_alluvium(aes(fill = Age_stress)) +
  geom_flow() +
  geom_stratum(aes(fill = Age_stress)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  #theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Age", "Duration", "Type"), expand = c(0.1, 0.1), position = "top") +
  ggtitle("Stress exposure variables (set2)")
```


### Alluvial diagrams for EE variables   

```{r alluvial plots EE, results = 'hide'}

# create frequency table for 3 categorical EE variables (EE_Type is not converted to HR)
freq_EE1 <- as.data.frame(table(dat_effect2$EE_exercise_HR, dat_effect2$EE_social_HR)) %>% rename(EE_exercise = Var1, EE_social = Var2)
is_alluvia_form(as.data.frame(freq_stress1), axes = 1:2, silent = TRUE)

ggplot(data = freq_EE1,
  aes(axis1 = EE_exercise, axis2 = EE_social, y = Freq)) +
  geom_alluvium(aes(fill = EE_exercise)) +
  geom_stratum(aes(fill = EE_exercise)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
#theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Exercise", "Social"), expand = c(0.15, 0.05), position = "top") +
  ggtitle("EE exposure  variables (set1)")


# create frequency table for 3 categorical EE variables
freq_EE2 <- as.data.frame(table(dat_effect2$Age_EE_exposure_HR, dat_effect2$EE_exercise_HR, dat_effect2$EE_social_HR)) %>% rename(Age_EE = Var1, EE_exercise = Var2, EE_social = Var3)
is_alluvia_form(as.data.frame(freq_EE2), axes = 1:3, silent = TRUE)

ggplot(data = freq_EE2,
  aes(axis1 = Age_EE, axis2 = EE_exercise, axis3 = EE_social, y = Freq)) +
  geom_alluvium(aes(fill = Age_EE)) +
  geom_flow() +
  geom_stratum(aes(fill = Age_EE)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  #theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Age", "Exercise", "Social"), expand = c(0.1, 0.1), position = "top") +
  ggtitle("EE exposure variables (set2)")


# create frequency table for another 3 categorical EE variables
freq_EE3 <- as.data.frame(table(dat_effect2$Type_EE_exposure_HR, dat_effect2$EE_exercise_HR, dat_effect2$EE_social_HR)) %>% rename(Type_EE = Var1, EE_exercise = Var2, EE_social = Var3)
is_alluvia_form(as.data.frame(freq_EE3), axes = 1:3, silent = TRUE)

ggplot(data = freq_EE3,
  aes(axis1 = Type_EE, axis2 = EE_exercise, axis3 = EE_social, y = Freq)) +
  geom_alluvium(aes(fill = Type_EE)) +
  geom_flow() +
  geom_stratum(aes(fill = Type_EE)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  #theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Type", "Exercise", "Social"), expand = c(0.1, 0.1), position = "top") +
  ggtitle("EE exposure variables (set3)")
```


### Alluvial diagrams for assay variables   

```{r alluvial plots assay, results = 'hide'}

# create frequency table for 3 categorical assay variables 
freq_assay1 <- as.data.frame(table(dat_effect2$Learning_vs_memory_HR, dat_effect2$Appetitive_vs_aversive_HR)) %>% rename(Learning_Memory = Var1, Reinforcement = Var2)
is_alluvia_form(as.data.frame(freq_assay1), axes = 1:2, silent = TRUE)

ggplot(data = freq_assay1,
  aes(axis1 = Learning_Memory, axis2 = Reinforcement, y = Freq)) +
  geom_alluvium(aes(fill = Learning_Memory)) +
  geom_stratum(aes(fill = Learning_Memory)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
#theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Learning_Memory", "Reinforcement"), expand = c(0.15, 0.05), position = "top") +
  ggtitle("Behavioural assay  variables (set1)")


# create frequency table for 3 categorical assay variables
freq_assay2 <- as.data.frame(table(dat_effect2$Age_assay_HR, dat_effect2$Learning_vs_memory_HR, dat_effect2$Appetitive_vs_aversive_HR)) %>% rename(Age_assay = Var1, Learning_Memory = Var2, Reinforcement = Var3)
is_alluvia_form(as.data.frame(freq_assay2), axes = 1:3, silent = TRUE)

ggplot(data = freq_assay2,
  aes(axis1 = Age_assay, axis2 = Learning_Memory, axis3 = Reinforcement, y = Freq)) +
  geom_alluvium(aes(fill = Age_assay)) +
  geom_flow() +
  geom_stratum(aes(fill = Age_assay)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  #theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Age", "Learning_Memory", "Reinforcement"), expand = c(0.1, 0.1), position = "top") +
  ggtitle("Behavioural assay  variables (set2)")


# create frequency table for another 3 categorical assay variables
freq_assay3 <- as.data.frame(table(dat_effect2$Type_learning_HR, dat_effect2$Learning_vs_memory_HR, dat_effect2$Appetitive_vs_aversive_HR)) %>% rename(Type = Var1, Learning_Memory = Var2, Reinforcement = Var3)
is_alluvia_form(as.data.frame(freq_assay3), axes = 1:3, silent = TRUE)

ggplot(data = freq_assay3,
  aes(axis1 = Type, axis2 = Learning_Memory, axis3 = Reinforcement, y = Freq)) +
  geom_alluvium(aes(fill = Type)) +
  geom_flow() +
  geom_stratum(aes(fill = Type)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  #theme_minimal() +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 3),
        axis.title.x = element_text(),
        axis.text.x = element_text(face="bold")) +
  scale_x_discrete(limits = c("Type", "Learning_Memory", "Reinforcement"), expand = c(0.1, 0.1), position = "top") +
  ggtitle("Behavioural assay  variables (set3)")
```



```{r assemble plots , results = 'hide'}
#p_F0_Parent_Exposed / p_Offspring_Sex / p_Trait + plot_layout(ncol = 1, heights = c(1,1,3))
#ggsave(file = "Figure_explorae_predictors_v0.pdf", width = 16, height = 23, units = "cm", dpi = 300, scale = 1.8,device = cairo_pdf)

# scale_fill_manual(values=c("#BAB3B3EB", "red", "yellow", "blue"))+ #note for manual colour assignment
#https://r-charts.com/flow/ggalluvial/
```
